---
title: "Datathon_final"
author: "ZM"
date: "2025-04-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(tidyverse)
library(readxl)
library(dplyr)
library(pwr)
library(lubridate)
library(logistf)
```

## Read excel sheets
```{r load data}
file_path <- "hh_dat_anonym_svk_final.xlsx" 

households <- read_excel(file_path, sheet = "Sheet1") 


file_path_2 <- "indv_dat_anonym_svk_final.xlsx" 

individuals <- read_excel(file_path_2, sheet = "Sheet1")
```


## calculate total number of children by enrollment
```{r enrollment counts}
# Filter only individuals under 18
children_filtered <- individuals %>%
  filter(DR_11_NUM_AGE_CAT1 %in% c("5 to 11", "12 to 17"))

# Count the number of children by enrollment status
education_enrollment_counts <- children_filtered %>%
  group_by(E0_SS_ENROLLED_HC) %>%
  summarize(
    Weighted_Count = sum(country_weight, na.rm = TRUE),
    .groups = "drop")


education_enrollment_counts <- education_enrollment_counts %>%
  rename(
    "Enrollment Status" = E0_SS_ENROLLED_HC,
    "Weighted Number of Children" = Weighted_Count)


print(education_enrollment_counts)
```

## create indicator columns for disability levels and age
```{r indicator columns}
individuals <- individuals %>%
  mutate(
    # Disability level 2: Includes "Some difficulty," "A lot of difficulty," or "Cannot do at all"
    disability_level_2 = if_else(WG_1_1_SS_DIFF_SEE %in% c("some_difficulty", "lot_difficulty", "cannot_all") |
                                WG_1_2_SS_DIFF_HEAR %in% c("some_difficulty", "lot_difficulty", "cannot_all") |
                                WG_1_3_SS_DIFF_WALK %in% c("some_difficulty", "lot_difficulty", "cannot_all") |
                                WG_1_4_SS_DIFF_REM %in% c("some_difficulty", "lot_difficulty", "cannot_all") |
                                WG_1_5_SS_DIFF_DRESS %in% c("some_difficulty", "lot_difficulty", "cannot_all") |
                                WG_1_6_SS_DIFF_COMM %in% c("some_difficulty", "lot_difficulty", "cannot_all"), 1, 0),

    # Disability level 3: Includes "A lot of difficulty" or "Cannot do at all"
   disability_level_3 = if_else(WG_1_1_SS_DIFF_SEE %in% c("lot_difficulty", "cannot_all") |
                                WG_1_2_SS_DIFF_HEAR %in% c("lot_difficulty", "cannot_all") |
                                WG_1_3_SS_DIFF_WALK %in% c("lot_difficulty", "cannot_all") |
                                WG_1_4_SS_DIFF_REM %in% c("lot_difficulty", "cannot_all") |
                                WG_1_5_SS_DIFF_DRESS %in% c("lot_difficulty", "cannot_all") |
                                WG_1_6_SS_DIFF_COMM %in% c("lot_difficulty", "cannot_all"), 1, 0)
  )



# Identify Children and Adults Based on Age Categories
individuals_categorized <- individuals %>%
  mutate(
    is_child = ifelse(DR_11_NUM_AGE_CAT1 %in% c("0 to 4", "5 to 11", "12 to 17"), 1, 0),
    is_adult = ifelse(!DR_11_NUM_AGE_CAT1 %in% c("0 to 4", "5 to 11", "12 to 17"), 1, 0)
  )

```


# -----------------------------------------------------------------------------
# PREPARATION FOR ANALYSIS
# -----------------------------------------------------------------------------

## Cleaning and preparation of Individuals data
```{r prep individuals}

survey_date <- as.Date("2024-07-01", format = "%Y-%m-%d")


# Select relevant columns from individuals data set
individuals_selected <- individuals %>%
    filter(DR_11_NUM_AGE_CAT1 %in% c("5 to 11", "12 to 17")) %>%  # Keep only children
    filter(E0_SS_ENROLLED_HC %in% c("yes", "no")) %>%  # Include only "yes" and "no" for enrollment
  select(
    unique_hh_index,
    gender = DR_12_SS_GEN,
    disability_level_3,
    disability_level_2,
    chronic_illness = H2_SS_HLTH_CHRONIC_ILL,
    psychological_issues = H11_SS_PSY,
    health_problem = H1_SS_HLTH_PBLM,
    language_skills = E0_SS_LANG_KNOWLEDGE,
    age = DR_11_NUM_AGE_CAT1,
    age2 = DR_11_NUM_AGE_CAT2,
    arrival_date = DR_15_NUM_INHC,
    E0_SS_ENROLLED_HC,
    individual_weight = country_weight,

  ) %>%
  mutate(
    
    # Health categorization
    health_issue = case_when(
      disability_level_3 == 1 | chronic_illness == "yes" | psychological_issues == "yes" | health_problem == "yes" ~ "yes",
      TRUE ~ "no"
    ),

    # Language skills grouping
    language_skills = case_when(
      language_skills %in% c("does_not_understand", "beginner", "intermediate") ~ "Low",
      language_skills %in% c("advanced", "fluent") ~ "High",
      TRUE ~ "Missing"
    ),

     # Convert arrival date to Date format
    arrival_date = as.Date(arrival_date, format = "%d.%m.%Y"),

    # Arrival Date Grouping (based on survey date)
   arrival_group = case_when(
  is.na(arrival_date) ~ NA_character_,  # Keep NA values as NA
  arrival_date >= survey_date - months(6)  ~ "In past 6 months",
  arrival_date >= survey_date - months(12) ~ "In past 1 year",
  arrival_date >= survey_date - months(24) ~ "In past 2 years",
  arrival_date >= survey_date - months(36) ~ "In past 3 years",
  TRUE ~ "Before past 3 years"
)
  )


```

## preparing HH head employment column
```{r}
# Identify Household Heads from individuals with all relevant employment-related variables
household_heads_raw <- individuals %>%
  filter(DR_16_SS_LEAD_HH == "yes") %>%
  select(
    unique_hh_index,
    DR_12_SS_GEN,
    SE2_SS_WORK,
    SE3_SS_BUSINESS,
    SE4_SS_FAM_BUSINESS,
    SE5_SS_HELP_FAM_BUSINESS,
    SE6_SS_TRY_FIND_JOB,
    SE7_SS_START_WORK_IN_2_WKS
  )

```


## Preparing columns with information on the head of HH 
```{r prep hh head}
# Identify household heads
household_heads_all <- individuals %>%
  select(
    unique_hh_index, iteration_hh, DR_16_SS_LEAD_HH,
    DR_12_SS_GEN, DR_11_NUM_AGE_CAT1, DR_11_NUM_AGE_CAT1,
    SE2_SS_WORK, SE3_SS_BUSINESS, SE4_SS_FAM_BUSINESS, SE5_SS_HELP_FAM_BUSINESS
  )

# Get household-level summaries of HH head responses
hh_head_flags <- household_heads_all %>%
  group_by(unique_hh_index) %>%
  mutate(
    num_yes = sum(DR_16_SS_LEAD_HH == "yes", na.rm = TRUE),
    
    # All said no or unsure (no one said yes)
    all_non_yes = all(DR_16_SS_LEAD_HH %in% c("no", "prefer_not_answer", "don't_know", NA)),

    pick_head = case_when(
      DR_16_SS_LEAD_HH == "yes" & num_yes == 1 ~ TRUE,                          # Single "yes"
      DR_16_SS_LEAD_HH == "yes" & iteration_hh == 1 ~ TRUE,                     # Multiple "yes", pick iter 1
      all_non_yes & iteration_hh == 1 ~ TRUE,                                   # All not yes, take iter 1
      TRUE ~ FALSE
    )
  ) %>%
  filter(pick_head) %>%  # Keep only selected HH head per logic above
  ungroup()

# Compute Employment & Gender
household_heads <- hh_head_flags %>%
  mutate(
    HH_Head_Gender = DR_12_SS_GEN,

    HH_Head_Employment = case_when(
      # Employed if yes to any relevant work question
      SE2_SS_WORK == "yes" | SE3_SS_BUSINESS == "yes" |
      SE4_SS_FAM_BUSINESS == "yes" | SE5_SS_HELP_FAM_BUSINESS == "yes" ~ "Employed",

      # Combine "Non-working age" and "Unemployed/Outside" into one category
      (DR_11_NUM_AGE_CAT1 == "60+" &
        is.na(SE2_SS_WORK) & is.na(SE3_SS_BUSINESS) &
        is.na(SE4_SS_FAM_BUSINESS) & is.na(SE5_SS_HELP_FAM_BUSINESS)) |
      (SE2_SS_WORK == "no" & SE3_SS_BUSINESS == "no" &
        SE4_SS_FAM_BUSINESS == "no" & SE5_SS_HELP_FAM_BUSINESS == "no") ~
        "Unemployed/Outside/non-working-age",

      TRUE ~ NA_character_
    )
  ) %>%
  select(unique_hh_index, HH_Head_Gender, HH_Head_Employment)


households_updated <- households %>%
  left_join(household_heads, by = "unique_hh_index")

```



## Preparing columns with information on the HH compositions - region and amount of adults + compile information on HH level

```{r hh composition}
household_regions <- households %>%
  mutate(
    Regions = case_when(
      INT04_SS_LOC_ADM1 %in% c("trnavsky", "trenciansky", "nitriansky", "bratislavsky") ~ "West",
      INT04_SS_LOC_ADM1 %in% c("zilinsky", "banskobystricky") ~ "Central",
      INT04_SS_LOC_ADM1 %in% c("presovsky", "kosicky") ~ "East",
      TRUE ~ "Other"
    )
  ) %>%
  select(unique_hh_index, Regions)

# Identify Adults in Each Household
household_adult_counts <- individuals %>%
  mutate(
    is_adult = ifelse(!DR_11_NUM_AGE_CAT1 %in% c("0 to 4", "5 to 11", "12 to 17"), 1, 0)  # Identify adults
  ) %>%
  group_by(unique_hh_index) %>%
  summarize(
    total_adults = sum(is_adult, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    hh_composition = case_when(
    total_adults == 1 ~ "One Adult",
    total_adults > 1 ~ "More Adults",
    TRUE ~ "No Adults"  # If no adults, specify category
  )
  )

# Merge Household Composition Info with Households Data
households_selected <- households %>%
  left_join(household_heads, by = "unique_hh_index") %>%  # Use preprocessed HH head info
  left_join(household_adult_counts, by = "unique_hh_index") %>%  # Add HH composition
    left_join(household_regions, by = "unique_hh_index") %>%  # Merged region grouping here
  select(
    unique_hh_index,
    accommodation = SHL01_1_SS_ACCOM_ARR,
    hh_head_gender = HH_Head_Gender,  # Already processed in household_heads
    bank_account = L12_SS_HV_BNK_ACC,
    hostile_behaviour = SC3_SS_EXP_HOSTILE,
    feeling_safe = PRT06_SS_SAFETY_LVL,
    hh_head_employment = HH_Head_Employment,  # Already processed in household_heads
    risk_girls = CP02_SM_RISK_G,
    risk_boys = CP01_SM_RISK_B,
    hh_composition,
    hh_weight = country_weight,
    Regions
  ) %>%
  mutate(
    # Accommodation grouping
    accommodation = case_when(
      accommodation %in% c("full_payment_by_household") ~ "Full payment by HH",
      accommodation %in% c("partial_payment_by_household", "partial_payment_by_household_sub_ngo", "partial_subsidized_by_emp", "partial_payment_hosted", "partial_payment_hosted_unrelated") ~ "Partial payment by HH",
      accommodation %in% c("no_payment_free_government", "no_payment_free_hosted", "no_payment_subsidized_by_emp") ~ "No payment by HH",
      TRUE ~ NA_character_
    ),
 # bank account
    bank_account = case_when(
      bank_account == "yes" ~ "yes",
      bank_account == "no" ~ "no",
      TRUE ~ NA_character_
    ),
 
  # hostile behaviour
    hostile_behaviour = case_when(
      hostile_behaviour == "yes" ~ "yes",
      hostile_behaviour == "no" ~ "no",
      TRUE ~ "Other"
    ),

    # Safety Level
    feeling_safe = case_when(
      feeling_safe %in% c("very_safe", "fairly_safe") ~ "yes",
      feeling_safe %in% c("bit_unsafe", "very_unsafe") ~ "no",
      TRUE ~ "Other"
    ),

  combined_risk = case_when(
  risk_girls == "no_concerns" | risk_boys == "no_concerns" ~ "No Risks",
  !is.na(risk_girls) & risk_girls != "no_concerns" ~ "Other Risks",
  !is.na(risk_boys) & risk_boys != "no_concerns" ~ "Other Risks",
  is.na(risk_girls) & is.na(risk_boys) ~ NA_character_
)

  )

# View the Updated Dataset
print(head(households_selected))

```

## Merge datasets

```{r merge}
# Merge datasets
A_clean_data <- individuals_selected %>%
  left_join(households_selected, by = "unique_hh_index")

# View the transformed dataset
print(head(A_clean_data))

```




# -----------------------------------------------------------------------------
# MULTIVARIATE LOGISTIC REGRESSION
# -----------------------------------------------------------------------------

```{r}
model <- glm(E0_SS_ENROLLED_HC ~ gender + language_skills + combined_risk + hostile_behaviour + health_issue + Regions  + accommodation + hh_head_gender + bank_account  + feeling_safe + hh_head_employment  + hh_composition, 
             data = A_clean_data, 
             family = binomial)
summary(model)

```
c sample needed for medium effectr size


```{r}
pwr.f2.test(u = 12,       
            v = NULL,     
            f2 = 0.15,    
            sig.level = 0.05,
            power = 0.80)
```



# -----------------------------------------------------------------------------
# DESCRIPTIVE TABLES
# -----------------------------------------------------------------------------


## Calculate enrollment percentage by gender of the child

```{r gender}

enrollment_gender <- A_clean_data %>%
    filter(!is.na(gender) & !is.na(E0_SS_ENROLLED_HC)) %>%  # Remove NA rows
  group_by(gender, E0_SS_ENROLLED_HC) %>%
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(gender) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(gender, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_gender)
```

## Calculate enrollment percentage by health status of child 

```{r health}

enrollment_grouped_health <- A_clean_data %>%
  group_by(health_issue, E0_SS_ENROLLED_HC) %>%
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(health_issue) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(health_issue, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_grouped_health)
```
## Calculate enrollment percentage by accommodation payment arrangements by Household

```{r accommodation}
# accommodation payment arragngement-related analysis
enrollment_accomm <- A_clean_data %>%
  group_by(accommodation, E0_SS_ENROLLED_HC) %>%
  filter(!is.na(accommodation) & !is.na(E0_SS_ENROLLED_HC)) %>%  # Remove NA rows
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(accommodation) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(accommodation, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_accomm)
```

## Calculate enrollment percentage by language skill of the child

```{r language}
enrollment_language <- A_clean_data %>%
  group_by(language_skills, E0_SS_ENROLLED_HC) %>%
  filter(!is.na(language_skills) & !is.na(E0_SS_ENROLLED_HC)) %>%  # Remove NA rows
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(language_skills) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(language_skills, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_language)
```

## Calculate enrollment percentage by gender of the Head of HH

```{r hh head gender}

enrollment_hh_head <- A_clean_data %>%
  group_by(hh_head_gender, E0_SS_ENROLLED_HC) %>%
  filter(!is.na(hh_head_gender) & !is.na(E0_SS_ENROLLED_HC)) %>%  # Remove NA rows
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(hh_head_gender) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(hh_head_gender, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_hh_head)
```
## Calculate enrollment percentage by HH composition

```{r hh compostion}
enrollment_hh_composition <- A_clean_data %>%
  group_by(hh_composition, E0_SS_ENROLLED_HC) %>%
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(hh_composition) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(hh_composition, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_hh_composition)
```

## Calculate enrollment percentage by employment status of the head of HH

```{r hh employment}

# employment of head of household-related analysis
enrollment_hh_employment <- A_clean_data %>%
    filter(!is.na(hh_head_employment) & !is.na(E0_SS_ENROLLED_HC)) %>%  # Remove NA rows
  group_by(hh_head_employment, E0_SS_ENROLLED_HC) %>%
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(hh_head_employment) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(hh_head_employment, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_hh_employment)
```

## Calculate enrollment percentage by wether the head of HH has a bank account

```{r bank}
enrollment_hh_bank <- A_clean_data %>%
    filter(!is.na(bank_account) & !is.na(E0_SS_ENROLLED_HC)) %>%  # Remove NA rows
  group_by(bank_account, E0_SS_ENROLLED_HC) %>%
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(bank_account) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(bank_account, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_hh_bank)
```

## Calculate enrollment percentage by households experiences of hostile behaviour from host community 
 
```{r hositle behaviour}
enrollment_hh_hostile <- A_clean_data %>%
    filter(!is.na(hostile_behaviour) & !is.na(E0_SS_ENROLLED_HC)) %>%  # Remove NA rows
  group_by(hostile_behaviour, E0_SS_ENROLLED_HC) %>%
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(hostile_behaviour) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(hostile_behaviour, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_hh_hostile)
```

## Calculate enrollment percentage by households percieved feelings of safety in their neighbourhood

```{r safety}

enrollment_hh_safety <- A_clean_data %>%
    filter(!is.na(feeling_safe) & !is.na(E0_SS_ENROLLED_HC)) %>%  # Remove NA rows
  group_by(feeling_safe, E0_SS_ENROLLED_HC) %>%
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(feeling_safe) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(feeling_safe, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_hh_safety)
```


## Calculate enrollment percentage by wether househols percieve any risks to children

```{r risk children}
enrollment_risk <- A_clean_data %>%
    filter(!is.na(combined_risk) & !is.na(E0_SS_ENROLLED_HC)) %>%  # Remove NA rows
  group_by(combined_risk, E0_SS_ENROLLED_HC) %>%
  summarize(
    Weighted_Count = sum(individual_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(combined_risk) %>%  
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  select(combined_risk, E0_SS_ENROLLED_HC, Weighted_Count, Percentage) %>%
  pivot_wider(names_from = E0_SS_ENROLLED_HC, values_from = c(Weighted_Count, Percentage), 
              names_glue = "{E0_SS_ENROLLED_HC}_{.value}")

# View the table
print(enrollment_risk)
```


## Calculate enrollment percentage by household region of residence

```{r hh region}
# Extract Region Information from Households Data
household_regions <- households %>%
  select(unique_hh_index, Region = INT04_SS_LOC_ADM1)  # Keep only necessary columns

#  Merge Region Data with Individuals Data
children_region_enroll <- individuals %>%
  filter(E0_SS_ENROLLED_HC %in% c("yes", "no")) %>%
  left_join(household_regions, by = "unique_hh_index")  # Add region info to each child

# Count Enrollment Status by Region
enrollment_by_region <- children_region_enroll %>%
  filter(!is.na(Region)) %>%  # Ensure region data is available
  group_by(Region, E0_SS_ENROLLED_HC) %>%
  summarize(
     Weighted_Count = sum(country_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(Region) %>%
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  pivot_wider(
    names_from = E0_SS_ENROLLED_HC,
    values_from = c(Weighted_Count, Percentage),
    names_prefix = "Enrolled_"
  )

# View the Final Table
print(enrollment_by_region)

```

## Calculate enrollment percentage by region of household - grouping regions ino east, west and central Slovakia

```{r hh region grouped}
# Extract and Group Region Information from Households Data
household_regions <- households %>%
  mutate(
    Grouped_Region = case_when(
      INT04_SS_LOC_ADM1 %in% c("trnavsky", "trenciansky", "nitriansky", "bratislavsky") ~ "West",
      INT04_SS_LOC_ADM1 %in% c("zilinsky", "banskobystricky") ~ "Central",
      INT04_SS_LOC_ADM1 %in% c("presovsky", "kosicky") ~ "East",
      
      TRUE ~ NA_character_  # Keep NA for missing/other regions
    )
  ) %>%
  select(unique_hh_index, Grouped_Region)

# Merge Grouped Region Data with Individuals Data
children_region_enroll <- individuals %>%
  filter( E0_SS_ENROLLED_HC %in% c("yes", "no")) %>%
  left_join(household_regions, by = "unique_hh_index")  # Add grouped region info to each child

# =Count Enrollment Status by Grouped Region 
enrollment_by_region <- children_region_enroll %>%
  filter(!is.na(Grouped_Region)) %>% 
  group_by(Grouped_Region, E0_SS_ENROLLED_HC) %>%
  summarize(
     Weighted_Count = sum(country_weight),  # Apply weights
    .groups = "drop"
  ) %>%
  group_by(Grouped_Region) %>%
  mutate(
    Percentage = (Weighted_Count / sum(Weighted_Count)) * 100
  ) %>%
  pivot_wider(
    names_from = E0_SS_ENROLLED_HC,
    values_from = c(Weighted_Count, Percentage),
    names_prefix = "Enrolled_"
  )

# View the Final Table
print(enrollment_by_region)

```



